Final Report Semester Project

### 2018-12-13 Final /Draft Visualizations Template.Rmd
Pushing changes

#Distribution of respondents reporting a mental disorder by age groups
ggplot(data = dfageprop, aes(x =Var2 , y = Freq, fill = Var1)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status based on age groups')
```

@@

```{r}
dfageprop1 <- as.data.frame(ageprop1)
ggplot(data = dfageprop1, aes(x =Var1 , y = Freq, fill = Var2)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')+ggtitle('Distribution of mental health status based on age groups')
```

>>>>

#Distribution of respondents reporting a mental disorder by age groups
ggplot(data = dfageprop, aes(x =Var2 , y = Freq, fill = Var1)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status across age groups')
```

@@

```{r}
dfageprop1 <- as.data.frame(ageprop1)
ggplot(data = dfageprop1, aes(x =Var1 , y = Freq, fill = Var2)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')+ggtitle('Distribution of mental health status across age groups')
```
